---
title: "EDA"
author: "Alejandro Muñoz"
date: "29/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# EDA of Spotify and Rolling-Stones data

## Objective:
Our objective is not to make predictions of any kind, we just want to understand how great songs and music are made and what they have in common. 

```{r}
library(ggplot2)
library(tidyr)
library(naniar) #Exploration of NAs
library(dplyr) #data manipulation
library(PerformanceAnalytics)#visualization of correlations
library(ggplot2)#ploting
library(ggpubr)#combine plots
```

Read files:

```{r}
rolling_stones <- read.csv('./Data/top500songsrollingstones.csv')
spotify <- read.csv("./Data/data_spotify_1921_2020.csv")

```

There is not much to explore in the data "500 Greatest Songs of All Time Rolling Stones". It is just a list of the songs and the authors. 
So, we will focus on the spotify data or the EDA.

First we will take a look at the distributions of songs over the years. 
```{r}
ggplot(spotify, aes(year)) + geom_histogram(bins = 100, color="darkblue", fill="lightblue" ) +
  ggtitle("Number of songs by year")

```

Now we will try to find correlations between variables and also seeing their distribution in the same plot by using the library *PerformanceAnalytics*.


```{r}
#first we take out all the variables that are not numeric
# and select the most relevant variables 
corr <- select(spotify, acousticness, danceability, energy, instrumentalness, popularity, valence, year)#selecciono solo variables numericas para generar plot
chart.Correlation(corr, histogram = TRUE, method = "pearson")
mtext("Spotify Data", side = 3, line = 1)
```




