---
title: "Join"
author: "Alejandro Muñoz"
date: "8/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyr)
library(naniar) #Exploration of NAs
library(dplyr) #data manipulation
library(ggplot2)#ploting
library(ggpubr)#combine plots
library(stringr)#manipulate strings
library(tidyverse)
library(reticulate)

`%!in%` <- Negate(`%in%`)
```


# Music analisiys 

On this notebbok we will try to bind two data frames into one to make music analisys. 
First we will try a join by column, but we expect problems with this because the name of the song may not be writen in the exact same way. 

To fix this we will try an aproximation using hashes and similarty measurments.


Read files:

```{r}
### Read data
rolling_stones <- read.csv('./Data/Top_500_songs.csv')
spotify <- read.csv("./Data/data_spotify_1921_2020.csv")
```

```{r}
### There are a lot of rows in the spotify dataset, we
### want to reduce it in order to make computations easier
nrow(rolling_stones)
nrow(spotify)
```

```{r}
### Remove everythging before 1947 and after 2008
rolling_stones <- rolling_stones |> 
  mutate(year = released |> str_sub(-4) |> as.integer()) |>
  filter(year > 1947)
spotify <- spotify |> 
  filter(year > 1947)
spotify <- spotify |> 
  filter(year < 2009)

### Remove those with strange characters
spotify <- spotify |>
  mutate(texto = paste(name, artists, sep = "    ")) |>
  mutate(texto = str_to_lower(texto)) |> 
  mutate(texto = str_remove_all(texto, pattern = "[^a-z -]")) |>
  filter(nchar(texto) > 10)
```

```{r}
words_to_remove <- c(
                     'Sonata', 'Danse', 'Remasterizado', 'Chapter',
                     'Nocturne', 'Prelude', 'Menuetto','Scherzando',
                     'Concerto',  'Instrumental', 'Quartet', 'Chorale',
                     'Mono', 'Concerto in', 'Bolero, No. 2',
                     'Fugue', 'Chanson', 'Corrido',

                     'Act I', 'Act II', 'Act III', 'Act IV',

                     'Op. 1', 'Op. 2', 'Op. 3', 'Op. 4',
                     'Op. 5', 'Op. 6', 'Op. 7', 'Op. 8',
                     'Op. 9', 'Op. 10', 'Op. 11', 'Op. 12',

                     'A Major', 'B Major', 'C Major', 'D Major',
                     'E Major', 'F Major', 'G Major',
                     'A Minor', 'B Minor', 'C Minor', 'D Minor',
                     'E Minor', 'F Minor', 'G Minor',

                     'No. 1', 'No. 2', 'No. 3', 'No. 4',
                     'No. 5', 'No. 6', 'No. 7', 'No. 8'
                     )


### Check if we are not removing something that does
### appear in the Rolling Stones dataset
rolling_stones_aux <- data.frame(rolling_stones)


for (word in words_to_remove){
  rolling_stones_aux <- rolling_stones_aux |> 
                  filter(!grepl(toupper(word), toupper(title)))
}

print(nrow(rolling_stones_aux) == nrow(rolling_stones))

### Remove the appearances of titles that contain these words
spotify_aux <- data.frame(spotify)

for (word in words_to_remove){
  spotify_aux <- spotify_aux |> 
                  filter(!grepl(toupper(word), toupper(name)))
}
```

```{r}
### Reassign to the spotify dataset
spotify <- data.frame(spotify_aux)

### Add index to reference later
rolling_stones$ID <- 1:nrow(rolling_stones)
spotify$ID <- 1:nrow(spotify)

nrow(spotify)
```



```{r}
#we create new columns to make the join by using hashes 

rolling_stones <- rolling_stones |>
                  mutate(texto = paste(title, artist, str_sub(released, start= -4) , sep = "    ")) |>
                  mutate(texto = str_to_lower(texto)) |> 
                  mutate(texto = str_remove_all(texto, pattern = "[^a-z -]")) |>
                  mutate(texto = paste(texto, str_sub(released, start= -4) , sep = "    "))

spotify <- spotify |> 
                  mutate(texto = paste(name, artists, sep = "    ") ) |>
                  mutate(texto = str_to_lower(texto)) |> 
                  mutate(texto = str_remove_all(texto, pattern = "[^a-z -]")) |>
                  mutate(texto = paste(texto, year , sep = "    "))
```



```{r}
# function to create hashes
calcular_tejas <- function(x, k = 4, lowercase = FALSE){
  tokenizers::tokenize_character_shingles(x, n = k, lowercase = lowercase,
    simplify = TRUE, strip_non_alpha = FALSE)
}

generar_hash <- function(){
  r <- as.integer(stats::runif(1, 1, 2147483647))
  funcion_hash <- function(tejas){
        digest::digest2int(tejas, seed = r) 
  }
  funcion_hash
}
```



```{r}
rolling_stones <- rolling_stones |> 
  mutate(tejas = map(texto, ~ calcular_tejas(.x, k = 6)))
spotify <- spotify |> 
  mutate(tejas = map(texto, ~ calcular_tejas(.x, k = 6)))
```



```{r}
set.seed(88345)
# crear hashes
hashes <- map(1:6, ~ generar_hash())

construir_firmas <- function(hashes, tejas){
  tibble(hash_num = 1:length(hashes), 
         firma = map_int(hashes, \(h) min(h(tejas)))
  )
}

rolling_stones_hashes <- rolling_stones |> 
  mutate(firma = map(tejas, ~ construir_firmas(hashes, .x))) |> 
  select(ID, firma) |> 
  unnest(firma) |> 
  mutate(cubeta = paste(hash_num, firma, sep = "-")) |> 
  select(ID, cubeta)

spotify_hashes <- spotify |> 
  mutate(firma = map(tejas, ~ construir_firmas(hashes, .x))) |> 
  select(ID, firma) |> 
  unnest(firma) |> 
  mutate(cubeta = paste(hash_num, firma, sep = "-")) |> 
  select(ID, cubeta)
```

Make join by hashes

```{r}
candidatos_tbl <- inner_join(rolling_stones_hashes |> rename(id_rolling_stones = ID), 
                          spotify_hashes |> rename(id_spotify = ID))
nrow(candidatos_tbl)
candidatos_tbl |> head(10)
```



```{r}
sim_jaccard <- \(a, b)  length(intersect(a, b)) / length(union(a, b)) 

candidatos_score_tbl <- candidatos_tbl |> 
  left_join(rolling_stones |>
              select(id_rolling_stones = ID, tejas_rolling_stones = tejas)) |> 
  left_join(spotify |> 
              select(id_spotify = ID, tejas_spotify = tejas)) |> 
  mutate(score = map2_dbl(tejas_rolling_stones, tejas_spotify, ~ sim_jaccard(.x, .y))) |> 
  select(-tejas_rolling_stones, -tejas_spotify, -cubeta)

candidatos_score_tbl <- candidatos_score_tbl |> 
  unique()

candidatos_score_tbl
```



```{r}
candidatos_score_tbl |> summarise(media_score = mean(score))
candidatos_score_tbl |> ggplot(aes(sample = score)) + geom_qq(distribution = stats::qunif)
```



```{r}
nrow(candidatos_score_tbl)
```



```{r}
candidatos_score_tbl |> arrange(desc(score))
```



```{r}
id_rolling_stones <- "158"
id_spotify <- "64896"
filter(rolling_stones, ID == id_rolling_stones) |> select(c(artist, title))
filter(spotify, ID == id_spotify) |> select(c(artists, name))
```



```{r}
candidatos_filt <- candidatos_score_tbl %>% filter(score > .3)

rolling_stones_filt <- rolling_stones %>%
  mutate(id_rolling_stones = ID) %>%
  mutate(title_rs = title) %>%
  mutate(artist_rs = artist) %>%
  select(c(id_rolling_stones, title_rs, artist_rs))

spotify_filt <- spotify %>%
  mutate(id_spotify = ID) %>%
  mutate(title_sp = name) %>%
  mutate(artist_sp = artists) %>%
  select(c(id_spotify, title_sp, artist_sp))

w <- merge(x = candidatos_filt, y = rolling_stones_filt, by = "id_rolling_stones")
w <- merge(x = w, y = spotify_filt, by = "id_spotify")
w <- w %>% select(-c( id_rolling_stones ))
w <- w |> select('id_spotify',	'score',	'title_rs', 'title_sp', 'artist_rs', 'artist_sp'	)
```



```{r}
### By artist
w |> 
  select(score, title_rs, title_sp, artist_rs, artist_sp) |>
  arrange(artist_rs, title_rs)
```


```{r}
### By score
w |> 
  select(score, title_rs, title_sp, artist_rs, artist_sp) |>
  arrange(desc(score))
```
We write it to a csv to work with it in python beacuse it is easier.

```{r}
write.csv(w, "./Data/top_500_matchs.csv")
```

Working on clean_top_500_matches.ipynb ...

Having worked in python, we read the new file.

```{r}
clean_top_500 <- read.csv("./Data/clean_top_500.csv")
```

```{r}
### Auxiliar code used to correct False Positives manually
#
# clean_top_500 |>
#   filter(id_spotify == 22203)
# 
# spotify |>
#   filter(grepl(toupper("Mississippi"), toupper(name)))  |>
#   select(c(ID, artists, name))
# 
# spotify |> 
#   filter(grepl(toupper("Beck"), toupper(artists))) |>
#   select(c(ID, artists, name))
```

We manually built a txt file containing all of the detected False Positives.

Note that there were some titles in the Rolling Stones dataset that
did not mactch with anything in the Spotify one.

```{r}
top_500_fp <- read.table("top_500_false_positives.txt", header=T)
top_500_fp <- top_500_fp |> drop_na()

top_500_fp
```

For every False Positive, we correct its true ID in Spotify:

```{r}
for(k in 1:nrow(top_500_fp)){
  
  new_aux <- spotify |> filter(ID == top_500_fp$true[k])
  new_artist <- new_aux |> pull(artists)
  new_title <- new_aux |> pull(name)
  
  clean_top_500["title_sp"][clean_top_500["id_spotify"] == top_500_fp$obs[k]] <- new_title
  clean_top_500["artist_sp"][clean_top_500["id_spotify"] == top_500_fp$obs[k]] <- new_artist
  clean_top_500["id_spotify"][clean_top_500["id_spotify"] == top_500_fp$obs[k]] <- top_500_fp$true[k]
  
}
```

Now we join this with the Spotify columns.

```{r}
rolling_stones_df <- clean_top_500 |> 
  select(id_spotify) |>
  left_join(spotify |> mutate(id_spotify = ID)) |>
  # select(-c(tejas, texto, ID, id)) |>
  select(-c(ID, id)) |>
  select(c("id_spotify", "artists", "name", "release_date", "year",
           "acousticness", "danceability", "speechiness", "tempo", 
           "valence", "energy", "instrumentalness", "liveness", 
           "loudness", "duration_ms", "popularity",
           "key", "mode", "explicit")) |>
  mutate(top_500 = T)

rolling_stones_df |> head()
```

Finally, we get a random sample of around 2500 songs from the Spotify dataset,
different to the ones in the final Rolling Stones df.

```{r}
set.seed(88345)

spotify_df <- spotify |> 
  subset(ID %!in% (rolling_stones_df |> pull(id_spotify))) |>
  sample_n(2500) |>
  select(-c(tejas, texto, id)) |>
  rename(id_spotify = ID) |>
  select(c("id_spotify", "artists", "name", "release_date", "year",
           "acousticness", "danceability", "speechiness", "tempo", 
           "valence", "energy", "instrumentalness", "liveness", 
           "loudness", "duration_ms", "popularity",
           "key", "mode", "explicit")) |>
  mutate(top_500 = F)

spotify_df |> head()
```

```{r}
final_df <- rbind(rolling_stones_df, spotify_df)
write.csv(final_df, "./Data/spotify_analysis.csv")
```
Last decade


```{r}
spotify_last <- read.csv("./Data/data_spotify_1921_2020.csv")

spotify_last <- spotify_last |> 
  filter(year > 2009)

### Remove those with strange characters
spotify_last <- spotify_last |>
  mutate(texto = paste(name, artists, sep = "    ")) |>
  mutate(texto = str_to_lower(texto)) |> 
  mutate(texto = str_remove_all(texto, pattern = "[^a-z -]")) |>
  filter(nchar(texto) > 10)

spotify_aux <- data.frame(spotify_last)

for (word in words_to_remove){
  spotify_aux <- spotify_aux |> 
                  filter(!grepl(toupper(word), toupper(name)))
}

### Reassign to the spotify dataset
spotify_last <- data.frame(spotify_aux)

### Add index to reference later
spotify_last$ID <- 1:nrow(spotify_last)
```

```{r}
set.seed(88345)

spotify_last_df <- spotify_last |> 
  subset(ID %!in% (rolling_stones_df |> pull(id_spotify))) |>
  sample_n(2500) |>
  select(-c(id)) |>
  rename(id_spotify = ID) |>
  select(c("id_spotify", "artists", "name", "release_date", "year",
           "acousticness", "danceability", "speechiness", "tempo", 
           "valence", "energy", "instrumentalness", "liveness", 
           "loudness", "duration_ms", "popularity",
           "key", "mode", "explicit")) |>
  mutate(top_500 = F)

spotify_last_df
```

```{r}
final_last_df <- rbind(rolling_stones_df, spotify_last_df)
write.csv(final_last_df, "./Data/spotify_analysis_last_decade.csv")
```

## First aproch: simple join
```{r}
rolling_stones$name <- rolling_stones$title

try_1 <- merge(x=rolling_stones,y=spotify,by="name",all.x=FALSE, all.y=FALSE)
nrow(try_1)
n_distinct(try_1$name)

try_1 |> select(name, title, artist, artists)
```
By doing this simple merge we find only 327 matches out of 500. And we enconuter a problem, there are many repetitions of the songs, aparently on the data base of spotify there are many cases in which for one specific song there are many versions of that same song. 

We will deal with the repetitions later, but first lets try to get 500 matches out of 500 by using hashes. 




